---
title: "HW 2"
author: "Iris"
date: "2018???5???9???"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


############ Q1 ########

########################

```{r}
# Set working directory
setwd("C:/Users/lenovo/Desktop/data driven/week 4/Individual 2")
email<-read.csv("Email_tracking.csv")
head(email)
summary(email)
```

#check if there is a difference in open rate by sending emails on different days from Sunday to Monday
```{r}
library(stringr)
class(email$Open_Rate)

op<-as.numeric(str_sub(email$Open_Rate,1,4))#input response variable
day<-email$Weekday #input factor
df<-data.frame(op=op,day=day) # create a data frame
aov<-aov(op~day,data=df) #analysis of variance
summary(aov)

```

#from the output,P-value=0.0162<0.05 which means it is reasonable to reject the null hypothesis. Therefore, there is a difference in open rate by sending emails on different days from Sunday to Monday.


```{r}

plot(op~day,data=df) #plot a box-plot
library(dplyr)

group_by(df, day) %>%
 summarise(mean=mean(op))
```
 
 #from the output, Wednesday (58.40476) has the highest mean of open rate.











############## Q2  ##########

################################


```{r}
# Set working directory
setwd("C:/Users/lenovo/Desktop/data driven/week 4/individual 2")
#import data directly
library(haven)
mmcase <- read_dta("mmcase.dta")
View(mmcase)
mmcase <-data.frame(mmcase)# convert tweets to a data frame
head(mmcase)
```
# business problem 5 needs to use log transforom for mmSales,mmprice,tpprice,trprice,sbprice

```{r}

mmcase$lmmsales<-log(as.numeric(mmcase$mmSales))
mmcase$lmmprice<-log(as.numeric(mmcase$pricemm))
mmcase$ltpprice<-log(as.numeric(mmcase$pricetropprem))
mmcase$ltrprice<-log(as.numeric(mmcase$pricetropreg))
mmcase$lsbprice<-log(as.numeric(mmcase$pricestore))

```

#fit the log-log sales model
```{r}

mod1<-lm(mmcase$lmmsales~mmcase$lmmprice+mmcase$ltpprice+mmcase$ltrprice+mmcase$lsbprice+mmcase$admm+mmcase$adtropprem+mmcase$adtropreg+mmcase$adstore)
summary(mod1)
```
#now, the adj R^2 is 0.7978.
# from the F-test, the p-value<0.05, therefore, this whole model is significant.




#new new control model with number of store assistants.
```{r}
mod2<-lm(mmcase$lmmsales~mmcase$lmmprice+mmcase$ltpprice+mmcase$ltrprice+mmcase$lsbprice+mmcase$admm+mmcase$adtropprem+mmcase$adtropreg+mmcase$adstore+mmcase$storeAssistants)
summary(mod2)
```
#from the F-test,the p-value<0.05 which means this model is significant.
#the adj-R^2 is 0.8355 which is higher than that of model 1 (0.7978). Therefore, model 2 is better.
# the number of store will affect this result.


```{r}
library(tinytex)
library(knitr)
```

