---
title: "Marketing Mix Modelling"
output: html_notebook
---
# Copyright of and Courtesy to Gabriel Mohanna

# Suppose we check the relationship of sales and advertisement directly
```{r}
sales <- c(37, 89, 82, 58, 110, 77, 103, 78, 95, 106, 98, 96, 68, 96, 157, 198, 145, 132, 96, 135)
ad <- c(6, 27, 0, 0, 20, 0, 20, 0, 0, 18, 9, 0, 0, 0, 13, 25, 0, 15, 0, 0)

modFit.0 <- lm(sales~ad)
summary(modFit.0)
```
# The R-squared value is very low. The model is not applausible. 


# Try looking at the variable distribution and consider using log transform
```{r}
plot(sales, ad)
hist(ad)
sales <- log(as.numeric(sales))

ad <-log(as.numeric(ad+1))

modFit.0 <- lm(sales~ad)
summary(modFit.0)
```



### Complexity 1: The Adstock Consideration
# Ad memory can be accumulated even though with diminishing effect. This is called ad stock.
# Let us assume every period will receive 50% memory effect of last period
# Sales = Base + b1·f(Advertising|α)

# where f() is a the adstock transformation function for the Advertising variable given an adstock of α.
# Other functional forms besides adstock can be incorporated here as well. 

```{r}
sales <- c(37, 89, 82, 58, 110, 77, 103, 78, 95, 106, 98, 96, 68, 96, 157, 198, 145, 132, 96, 135)
ad <- c(6, 27, 0, 0, 20, 0, 20, 0, 0, 18, 9, 0, 0, 0, 13, 25, 0, 15, 0, 0)

ad.adstock <- as.numeric(filter(x=ad, filter=.50, method="recursive"))
ad.adstock

modFit.1 <- lm(sales~ad.adstock)
summary(modFit.1)
```
# Notice how we improved R2 from 0.184 to 0.252. But there are more reasons to be discovered


#Complexity 2: More Advertising Variables
```{r}
sales <- c(37, 89, 82, 58, 110, 77, 103, 78, 95, 106, 98, 96, 68, 96, 157, 198, 145, 132, 96, 135)
tv <- c(6, 27, 0, 0, 20, 0, 20, 0, 0, 18, 9, 0, 0, 0, 13, 25, 0, 15, 0, 0)
online <- c(3, 0, 4, 0, 5, 0, 0, 0, 8, 0, 0, 5, 0, 11, 16, 11, 5, 0, 0, 15)

tv.adstock <- as.numeric(filter(x=tv, filter=.3, method="recursive"))
online.adstock <- as.numeric(filter(x=online, filter=.3, method="recursive"))

modFit.2 <- lm(sales~tv.adstock+online.adstock)
summary(modFit.2)
```
# Now, our model is even stronger with R2 of 0.769.


# Complexity 3: Changing Base & Other Variables
# So far we assumed the Base to be a constant. But it is not always constant. For example, the growth of population may lead to a trend for sales growth.  
# Other variables should be considered:
# Seasonal variables 
# Distribution points
# Pricing changes

```{r}
sales <- c(37, 89, 82, 58, 110, 77, 103, 78, 95, 106, 98, 96, 68, 96, 157, 198, 145, 132, 96, 135)
tv <- c(6, 27, 0, 0, 20, 0, 20, 0, 0, 18, 9, 0, 0, 0, 13, 25, 0, 15, 0, 0)
online <- c(3, 0, 4, 0, 5, 0, 0, 0, 8, 0, 0, 5, 0, 11, 16, 11, 5, 0, 0, 15)
trend <- 1:20

tv.adstock <- as.numeric(filter(x=tv, filter=.3, method="recursive"))
online.adstock <- as.numeric(filter(x=online, filter=.3, method="recursive"))

modFit.3 <- lm(sales~trend+tv.adstock+online.adstock)
summary(modFit.3)
```
# Model has a good fit with R-squared value at 0.94

# Every 2.17 units of TV will have 1 unit of sales increase
# Every 2.98 units of online ad will have 1 unit of sales increase
# TV is more efficient than online in stimulating sales




