---
title: "R Notebook"
output: html_notebook
---
# set working directory with your own location
```{r}
setwd("/Users/Tao/Dropbox/Teaching/BAMA517_personal/Dataset")
```
# Load the package
```{r}
library(igraph)
#library(sna)
```

# get the data in edge list format
```{r}
g1 <- read.table('undirected.txt')
g2 <- read.table('directed.txt')

head(g1)
```

# create graph for g1
```{r}
graph1 <- graph_from_data_frame(g1, directed = FALSE, vertices = NULL)
plot(graph1)
```

# arrow is too big
```{r}
graph2 <- graph_from_data_frame(g2)
plot(graph2, directed = TRUE, vertices = NULL)
```

# create a full network
```{r}
g_full <- make_full_graph(8, directed = FALSE)
plot(g_full)
```

# create a empty network
```{r}
g_empty <- make_empty_graph(40)
plot(g_empty)
```

# create a ring graph
```{r}
g_ring <- make_ring(12, directed = FALSE, mutual = FALSE)
plot(g_ring)
```

# create a star graph
```{r}
g_star <-make_star(10, center = 1)
plot(g_star)
```

# create a tree graph
```{r}
tr <- make_tree(40, children = 3, mode = "undirected")
# try differen parameters to design the look
plot(tr, vertex.size=10, vertex.color = "purple", vertex.label=NA)
plot(tr, vertex.size=10, vertex.color = "purple", vertex.label.color="white") 

tr <- make_tree(40, children = 3, mode = "undirected") %>%
  set_vertex_attr("color", value = "green") %>%
  set_edge_attr("color", value ="blue")
plot(tr)
```

# build a graph with 20 nodes and 30% connectedness
```{r}
g_gnp <- sample_gnp(20, 0.3, directed = FALSE, loops = FALSE)
plot(g_gnp)
```

# build a graph with 20 nodes and 50 edges (randomly connected)
```{r}
g_gnm <- sample_gnp(20, 0.5, directed = FALSE, loops = FALSE)
plot(g_gnm)
```

# build a graph with 20 nodes and 50 edges (randomly connected)
```{r}
g_gnm <- sample_gnp(20, , directed = FALSE, loops = FALSE)
plot(g_gnm)
```

# build a preferential attachment graph with 20 nodes and the node with one
# more edge is the priority to attract others
```{r}
g_gpa <- sample_pa(20, power =1)
plot(g_gpa)
```

######Calculating Network Measures########

```{r}
library(igraph)
g1 <-sample_pa(12, power =1, directed = FALSE)
plot(g1)
```

# degree means the number of edges of each node
```{r}
degree(g1)
```

# in- and out-degree centrality score for directed network
```{r}
g2 <- read.table('directed.txt')
graph2 <- graph_from_data_frame(g2)
degree(graph2, mode = "in")
degree(graph2, mode = "out")
```

# betweenness centrality
```{r}
g1 <- sample_pa(20, power =1, directed = FALSE)
plot(g1)
betweenness(g1)
```

# network density
```{r}
ed <- edge_density(g1, loops=FALSE)
ed
```

# try another one
```{r}
g2 <- sample_pa(40, power =1, directed = FALSE)
plot(g2)
ed2 <- edge_density(g2, loops=FALSE)
ed2
```

## The density of preferential attachment framework is 2 divided by number of nodes
## This is because this type of network adds one more edge with one more node

# gnp graph's density
```{r}
gnp <- sample_gnp(20, 0.3, directed = FALSE, loops = FALSE )
plot(gnp)
edg <-edge_density(gnp, loops = FALSE)
edg
# Everytime the density may be different but all around 0.3 (as we defined it!)
```

## Identify the cliques in a graph
# cliques are the fully connected clusters in the network - "small circles"
```{r}
gnp <- sample_gnp(20, 0.3, directed = FALSE, loops = FALSE )
plot(gnp)
clique_num(gnp)
```

# you want to see only the cliques with four more edges
```{r}
cliques(gnp, min = 4)
```

# you can set the range of number of edges for cliques  
```{r}
cliques(gnp, min = 3, max = 4)
```

# let's increase the density
```{r}
gnp <- sample_gnp(20, 0.3, directed = FALSE, loops = FALSE )
clique_num(gnp)
```

# Find components of a graph
# A component is a gropu of connected network nodes. 
# A graph may have multiple components that are not interconnected. 
```{r}
gnp <- sample_gnp(20, 0.08, directed = FALSE, loops = FALSE )
plot(gnp)
components(gnp)
```

# Take a random walk on a graph
```{r}
g1 <- sample_gnp(30, 0.08, directed = FALSE)
plot(g1)
```

#First number is the starting point. The second number is how may stops you plan.
```{r}
random_walk(g1, 15, 8, stuck = "return")
# Use of the random walk? Twitter use it for recommeding who to follow.
```

# Saving the graph file
```{r}
g1 <- sample_gnp(30, 0.08, directed = FALSE)
plot(g1)
write.graph(g1, file='rand_network.txt', format = "edgelist")
```






